Using numerical modelling to investigate temperature and wave exposure as drivers of macroalgal characteristics

### 2019-08-04 morphology_paper.Rmd
script for extra graph created

temp_boxplot <- ggplot(data = temp_ann_meta, aes(x = region, y = mean_temp, fill  = region)) + 
  geom_boxplot() + 
  scale_x_discrete(limit = c("Western", "Eastern")) + 
  stat_compare_means() + 
  xlab("") + 
  ylab("")

@@

wave_plot_B <- ggplot(data = wave_ann, aes(x = site, y = tp_mean)) +
  geom_point() + 
  scale_x_discrete(limits = positions_wave) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5)) +
  geom_errorbar(aes(x = site, ymin = tp_mean - tp_sd, ymax = tp_mean + tp_sd)) + 
  xlab("") + 
  ylab("") + 
  theme(legend.position = "none") + 
  theme(plot.title = element_text(hjust = 0)) + 
  coord_flip() 
```

```{r wave variable plot, warming = FALSE, echo=FALSE, message = FALSE, include= TRUE, fig.cap='Wave variables at each collection site around the Western Cape coast. Mean variables are represented by dots and standard deviation by whiskers.'}
ggarrange(wave_plot_A, wave_plot_B, ncol = 2, nrow = 1)
```

>>>>

temp_boxplot <- ggplot(data = temp_ann_meta, aes(x = region, y = mean_temp, fill  = region)) + 
  geom_boxplot() + 
  scale_x_discrete(limit = c("Western", "Eastern")) +
  scale_fill_discrete(name="Region") +
  stat_compare_means() + 
  xlab("") + 
  ylab("")

@@

wave_plot_B <- ggplot(data = wave_ann, aes(x = site, y = tp_mean)) +
  geom_point() + 
  scale_x_discrete(limits = positions_wave) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5)) +
  geom_errorbar(aes(x = site, ymin = tp_mean - tp_sd, ymax = tp_mean + tp_sd)) + 
  xlab("") + 
  ylab("") + 
  theme(legend.position = "none") + 
  theme(plot.title = element_text(hjust = 0)) + 
  coord_flip()

wave_ann_meta <- merge(meta_all, wave_ann, by = "site")
wave_ann_meta$site <- as.character(wave_ann_meta$site)

wave_boxplot_1 <- ggplot(data = wave_ann_meta, aes(x = region, y = hs_mean, fill  = region)) + 
  geom_boxplot() + 
  scale_x_discrete(limit = c("Western", "Eastern")) + 
  scale_fill_discrete(name="Region") +
  stat_compare_means() + 
  xlab("") + 
  ylab("")

wave_boxplot_2 <- ggplot(data = wave_ann_meta, aes(x = region, y = tp_mean, fill  = region)) + 
  geom_boxplot() + 
  scale_x_discrete(limit = c("Western", "Eastern")) +
  scale_fill_discrete(name="Region") +
  stat_compare_means() + 
  xlab("") + 
  ylab("")
```

```{r wave variable plot, warming = FALSE, echo=FALSE, message = FALSE, include= TRUE, fig.cap='Wave variables at each collection site around the Western Cape coast. Mean variables are represented by dots and standard deviation by whiskers.'}
ggarrange(wave_plot_A,wave_boxplot_1, wave_plot_B, wave_boxplot_2, common.legend = TRUE, labels = c("AUTO"))
```
